Neural and Symbolic Spatiotemporal Optimization of Cosmological Particle-Mesh Simulation

### 2023-03-11 docs/papers/sto/sto.tex
FIXUP draft: edit TODOs

\section*{TODO}
\begin{itemize}
\item Compare one pair of Gadget4 and \pmwd\ (with say 100 to 1000 time
    steps) results and make sure that they agree perfectly on the large
    scales. For this purpose the box size should be large enough (in
    linear regime), say 1 Gpc/$h$.
    \textbf{Update: for Sobol=6, boxsize=983Mpc, Gadget4 and \pmwd\ are visually
    consistent at the field level. To further check power spectrum.}
\item Be careful with the non-deterministic ICs generated on GPUs.
      \textbf{Update: we have shown that ICs generated on GPUs are deterministic
      (but different from those on CPUs), generating ICs for both training data
      and training on GPUs might be the simplest solution.}
  \begin{enumerate}
  \item Saving them on disks and loading them during training solves
    this but may introduce IO or memory problem;
  \item Generating them on CPUs for training data and also training
    might suffice while requireing such data loader implementation;
  \item Generating them on GPUs for training data and training will
    introduce additional source of initial deviations to be nonlinearly
    amplified. There are flags that makes certain operations
    deterministic but slow on GPUs, but those are enviroment variables
    that function globally and cannot be applied locally only on the IC
    generation during training.
  \item Generating ICs and then train on GPUs with double precision and
    then compute the loss at single precision (Gadget4 should be run at
    double precision) should work, and likely be the simplest solution.
    But for this to work the final training loss should be much larger
    than the level of reproducibility.
  \end{enumerate}
\item Non-integer multiple mesh shapes: for uniform particle grid, test
  (with double precision on CPUs) whether they start moving by artifact
  forces on cell scales, in 3 cases: no deconvolution, with CIC
  deconvolution, with SO.
\item For TO, probably necessary to first incorporate Oliver Hahn's
  recent improvement on FastPM integrator arXiv:2301:09655.
\end{itemize}

>>>>

\section*{TODO}
\begin{itemize}
\item Moving some of the following ongoing and completed tasks to the
    main text and add preliminary figures.
\item Implement the rest of the nonlinear scales, including the rms
    displacement with np.trapz of $P$ over $\ln k$, the $\ln a$ time
    derivatives, etc.
\item Compare one pair of Gadget4 and \pmwd\ (with say 100 to 1000 time
    steps) results and make sure that they agree perfectly on the large
    scales. For this purpose the box size should be large enough (in
    linear regime), say 1 Gpc/$h$.
    \textbf{Update: for Sobol=6, boxsize=983Mpc, Gadget4 and \pmwd\ are visually
    consistent at the field level. To further check power spectrum.}
\item Be careful with the non-deterministic ICs generated on GPUs.
      \textbf{Update: we have shown that ICs generated on GPUs are deterministic
      (but different from those on CPUs), generating ICs for both training data
      and training on GPUs might be the simplest solution.}
\item Non-integer multiple mesh shapes: for uniform particle grid, test
  (with double precision on CPUs) whether they start moving by artifact
  forces on cell scales, in 3 cases: no deconvolution, with CIC
  deconvolution, with SO.
\item For TO, probably necessary to first incorporate Oliver Hahn's
  recent improvement on FastPM integrator arXiv:2301:09655.
\end{itemize}
